---
title: "First R Markdown"
author: "CC"
date: "November 20, 2016"
output: ioslides_presentation
---

## My new slide
Some content


## My title

- Bullet one
- Bullet two

1. Item a
2. Item b

## My new slide 2

Plain Text 

*italicized text*

**Bold text**

`for (i %in% 1:10)`

## My new slide 3
```{r, comment="", echo=FALSE}
head(mtcars)

```

## My new slide 4 
```{r,echo=FALSE, fig.align='center',fig.cap='My AWESOME figure'}
plot(mtcars$wt,mtcars$mpg,xlab="Weight",ylab="MPG")
```



## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

